Ae. albopictus CPP manuscript

### 2020-02-24 MS.Rmd
Better maps

```{r table1, echo=FALSE}
kable(filter(pops, only_2008=="n")[,1:6], col.names=c("Population", "City", "Latitude", "Longitude", "Country", "Life Stage Sampled"), caption="Table 1: 2018 Sampling Locations")
```

@@

country_DI_bw
```
```{r echo=FALSE, warning=FALSE}
ggplot(filter(DI_short_2, year!=1988), aes(x=lat, y=DI, fill=country, shape=year)) + scale_fill_manual(values=c("black","gray"), name="Country") + scale_shape_manual(values=c(21,24), name="Year") + geom_point(size=3) + theme_bw() + theme(legend.position=c(0.9,0.3), text=element_text(size=12)) + guides(fill = guide_legend(override.aes=list(shape=22))) + xlab("Latitude") + ylab("Short-day diapause incidence") + geom_smooth(aes(linetype=year, color=country), se=FALSE, method="glm", method.args=list(family="binomial")) + scale_linetype_manual(values=c("dotted","solid"), name="Year") + scale_color_manual(values=c("black","gray"), name="Country")

>>>>

```{r table1, echo=FALSE}
kable(filter(pops, only_2008=="n")[,1:7], col.names=c("Population", "City", "Latitude", "Longitude", "Country", "Generation*", "Life Stage Sampled"), caption="Table 1: 2018 Sampling Locations")
```

@@

country_DI_bw
```
```{r echo=FALSE, warning=FALSE}
di_plot_binomial<-ggplot(filter(DI_short_2, year!=1988), aes(x=lat, y=DI, fill=country, shape=year)) + scale_fill_manual(values=c("black","gray"), name="Country") + scale_shape_manual(values=c(21,24), name="Year") + geom_point(size=3) + theme_bw() + theme(legend.position=c(0.9,0.3), text=element_text(size=12)) + guides(fill = guide_legend(override.aes=list(shape=22))) + xlab("Latitude") + ylab("Short-day diapause incidence") + geom_smooth(aes(linetype=year, color=country), se=FALSE, method="glm", method.args=list(family="binomial")) + scale_linetype_manual(values=c("dotted","solid"), name="Year") + scale_color_manual(values=c("black","gray"), name="Country")
